%-----------------------------------------------------------------------
%\subsection{Mode and Level}
%-----------------------------------------------------------------------
%\tbc
%

\section{Motivation}
%\tbc
%BaseliyosJacob
The openETCS work package 3 (WP3) aims to provide – amongst others - the software architecture for the openETCS kernel in order to eventually build the software itself. WP3  partner has put great effort in the openETCS software design, thus far without making definite choices on the software architecture itself respective of functional breakdown and data structures of the openETCS kernel. Since the project planning foresees in the production of a reference software to be used as a demonstrator by June 2015, it is of paramount importance that a first design delivarable of the openETCS kernel architecture be finalized shortly but no later than November 2014.\\

In compliance with the agreements made during the last WP 3 meeting at the 10.09.2014 in Brussels, DB has taken the initiative to design the aforesaid architecture including of functional breakdown and data structures in order to safeguard a timely delivery of these products. Furthermore, DB has ensured that these developments are focused on including end user requirements so as to develop a design in conformity with the needs and requirements of the operators. Specialists of DB and NS have cooperated together with other partners in WP3 to produce this document.\\

As referred to above, the architecture description has to be finalized in the month of November 2014. This version of the document is a draft version, demonstrating the general directions and philosophy of the architectural design, the functional breakdown of the software and the data structures. The design is focused on maximum efficiency in order to maximize on RAMS performance of the end product.\\


\section{Objectives}
%\tbc
%Baseliyos Jacob
The prime objective of WP3 is to produce a fully formal prototype for the openETCS reference system that can function as a demonstrator in collaboration with WP 4 and WP 5  for the openETCS approach and will be used as such in the final phase of the project. That phase is the first half of 2015.  This objective is defined as … 

\textbf{High level Objectives of this work:}
<<any further general statements on the ITEA2  objectives, like…>>\\

\begin{itemize}
\item Work on a model bases approach and process for effective collaborative work within an international ETCS developer team as stated above, the project needs a definite architecture design by the end of 2014.

\textbf{This document targets:}
\item Defining the general design and conditions of the openETCS architecture, functional breakdown and data structures
\item Providing the guidelines for discussion during the workshops that are planned in October and November 2014 that will result in the final and decisive version of this document
\item Being the ‘platform’ for finalization i.e. whatever be the products or results of the workshops shall be integrated in this document.

\textbf{Apart from these general objectives, the document means to provide for the materials that will enable WP3 partners to improve the efficiency of the Work Package activities:}
\item The comprehensive architecture design shall enable splitting the work load according to the building blocks defined by the architecture and allocate strictly compartmented work parcels or activities to WP3 partners.
\item Doing so will enable WP3 to avoid any double work
\item  Compartmenting the work load according to the functional building blocks as defined by the architecture will enable efficient planning of activities, be it individually or the integrated WP3 planning for the coming period, aiming at a just in time delivery of all results and products
\item  Compartment the work load according to the functional building blocks as defined by the architecture will enable efficient planning of activities, be it individually or the integrated WP3 planning for the coming period, aiming at a just in time delivery of all results and products
\end{itemize}

\section{Roles, responsibilities and tasks}
%\tbc
%Baseliyos Jacob
\textbf{In this section, the roles and responsibilities of the WP3 partners are confirmed, especially where they divert from what has been agreed upon at the start of WP3:}

\begin{itemize}
\item\textbf{Responsibilities} First of all, in the last WP 3 meeting in Brussels on  10.09.2014 DB proposed to take over the lead of the architecture design and functional breakdown. At the subsequent weekly scrum meeting on 12.09.2014,  it was agreed upon by all participants that DB will take over the lead (see Appendix … );\\
\item\textbf{Planning:} Alstom as WP 3 leader will remain to be responsible for the planning and the allocation of the defined tasks to the different partners\\
\item\textbf{Roles:} Alstom will also coordinate the work and safeguard that the defined results will be delivered according to the quality requirements that are agreed within the ITEA2 project and the schedule and the milestones that will be agreed upon during the coming workshops;\\
\item All WP3 partners will deliver the results or products according to planning as will be agreed upon during the said workshops. \\

In the interest of a swift production of the critical documentation of which this version is a draft, specific tasks will be defined in terms of concrete results to be delivered, the timeframes in which these results must be produced and the partner who shall be responsible for that specific result and the planning. This is to safeguard the timely delivery. The process will be described in the next sections.\\
\end{itemize}

\section{Process}
%\tbc
%JakobGärtner
\begin{itemize}
\item\textbf{Alstom as WP 3 leader will be responsible for planning}
\item\textbf{Time and quality aspects should be respected}
\item\textbf{openETCS tools and methodology must be respected}


\textbf{Most of the operational requirements to WP3 in the last phases of the ITEA2 project have been described in the former paragraphs. This section will describe the process which has to lead to the final result: the reference software to be used in the demonstrator next year, more specifically the final description of the openETCS architecture including the data structures and its functional decomposition. The process will run as follows:}

\item DB will supervise  the development of the first ‘firm’ draft of the specified products, ‘firm’ meaning that changes can only be made within the framework of these products and not to the fundamentals of these products as described in this document

\item DB will supervise the preparation of the two workshops that are proposed by Alstom and aim at defining the final and definite architecture, data structures and functional decomposition. It will make proposals for a planning of the critical tasks that remain to be done
\item Alstom will lead the two workshops following the preparations and the instructions of DB. Since all participants are intrinsically involved in the development work and tend to immerse themselves in technical discussions, for productivity purposes it is proposed to make use of a (non-technical) moderator that will be made responsible for coordinating the meeting, the discussions and the team efforts according ot the agenda.\\
\item Also for productivity reasons, introductory presentations will be restricted to the contents and setup of this document since all prior efforts have to be merged with this document and not the other way around. Following a general introduction into the work that has been so far, the other contributions will be scrutinized on their consistency with this document and any useful sections will be merged with this document.\\
\item During the workshops, there will be ample room reserved for enhancing this document, using other documents pertaining to the same field of work that have been delivered by other partners. Only material that is aligned with the general philosophy and structures proposed by this document, will be integrated;\\
\item In case conflicting views emerge over the benefits and value of certain contributions, at the very moment that parties conclude that they have conflicting views, these will be listed in an inventory for later discussion. The moderator shall note any such conflicts on the said inventory. Conflicting views will be treated at the end of each workshop whenever there is sufficient time or will be treated in a separate meeting that will be chaired by DB as coordinator of the ITEA2 project.\\
\item The workshop shall be attended by a secretary provided for by DB who is responsible for making the workshop minutes. Within a week after each workshop these minutes shall be distributed among the partners that have cooperated in the workshop and be reviewed by those. \\
\item The main objective of the workshops shall be the finalization of this document. In order to reach the specified result, the remaining tasks shall be identified and split into separate tasks or work parcels. Every task or work parcel will be allotted to one single responsible partner. Responsibility relates to the timely delivery of the defined result and according to quality requirements;\\
\item Alstom, as WP3 leader, will be responsible for the planning, allocation of tasks or work parcels to partners and will ensure timely delivery of results;\\
\item In case there will be tasks or work packages that cannot be finalized during the workshops or will be identified during the workshops and do not fit in the actual planning, these will be allotted in such a way that deadlines are perfectly clear and acknowledged by the party that is responsible for the results, fit within the general requirements of the project and are agreed upon in writing and executed by the responsible partners according to agreement;\\
\item DB as partner that has integral responsibility for both the ITEA2 project and responsible as well for the architecture etc. , is entitled to interfere take over the role as leader / coordinator in case the workshops prove to be insufficiently productive;\\
\item All output will be such, that it can be integrated in this document. It is the responsibility of DB to integrate the results and to deliver the final and definite version of this document. \\
\item The document concept will follow the openETCS process and tools (LaTex and Git-hub).\\

\end{itemize}

\section{Assumptions and preconditions}
%\tbc
%Baseliyos Jacob
\begin{itemize}
\item All future contributions shall be fully aligned an compliant the finalized and approved document 
\item Alls documents produced by the partners are requested to be compliant and merge to this document; other contributions will be discarded
\textbf{The workshops are all about working as swift, as efficient and as productive as possible and make full use of the potential made available for these workshops by the partners. It is expected that the partners in the workshops will have the express intention to:}
\item Contribute to the workshops with the intention to finalize the openETCS architecture;\\
\item Provide resources according to the agreements made prior to the Workshops;\\
\item Focus primarily on  getting concrete results regardless of methodological issues that might arise. Where necessary or opportune, classical project management methodology will be applied;\\
\item Provide full transparency with respect to experience, knowledge base and information touching the subjects to be treated in the workshops;\\
\item Document on paper or electronically all output of the workshops and integrate these with the underlying document;\\
\item Restrict discussions only to topics that have an immediate impact on the content or the quality of the end product: the improved version of this document.\\
\end{itemize}

\section{openETCS history and iterations}
%\tbc
%BaseliyosJacob
The openETCS Architecture and Design wil implemented in iterations. The current step (third iteration) is based on a step to implement the kernel functions of the ETCS system. For a better understanding of the scope the Iteration is described in the following.

\textbf{Third Iteration Functional Scope: The OBU functions for Szenarios defined in chapter 3}

The openETCS third iteration architecture and the design of the openETCS OBU software as mainly specified in \cite{subset-026} UNISIG Subset\_026 version\_3.3.0. 

The appropriate functionality has been divided into a list of functions of different complexity to make it more managable by the different designer.

All these functions are object of the openETCS project and have to be analysed from their requirements and subsequently modelled and implemented. With the given manpower in WP 3, a reasonable selection and order of these functions is required for the practical work that allows the distribution of the workload, more openETCS participants to join and leads to an executable---limited---kernel function as soon as possible. 


\textbf{The first objective of this third iteration are:}
\begin{itemize}
\item ``Make the train run as soon as possible, on the scenarios defined in third iteration \textbf(see chapter 3), and in the form of a rapid prototype".
This does not contradict the openETCS goal to conform to EN50128.
\item After a phase of prototyping, the openETCS software shall be implemented in compliance to EN50128 for SIL4 systems.
\end{itemize}


