%set the master document for easy compilation
%!TEX root = ../D3_5_3.tex

\paragraph{Component Requirements}

\begin{longtable}{p{.25\textwidth}p{.7\textwidth}}
\toprule
Component name			& CheckBGConsistency \\
\midrule
Link to SCADE model		& {\footnotesize \url{https://github.com/openETCS/modeling/tree/master/model/Scade/System/ObuFunctions/ManageLocationRelatedInformation/BaliseGroup/CheckBGConsistency}} \\
\midrule
SCADE designer			& Peyman Farhangi, DB Netz AG \\
\midrule
Description				& The function "Receive\_TrackSide\_Msg" collects the telegrams in an
array. If one or more telegrams are received multiple times, either the whole the array or single telegram should be deleted.(e.g.if the train moves back.) The balises in a group are to be expected in a certain distance from each other. The function "Receive\_TrackSide\_Msg" checks if the telegrams has been received in due time and at the right expected location.
\\
&
The function "CheckBGConsistency" verifies the completeness and correctness of the received telegrams from balise groups and composes the balise message from the received telegram array (input from "Receive\_TrackSide\_Msg"). A balise message is built from at least one telegram and a maximum of 8 telegrams. When linking information is used on-board, only balise groups marked as linked and included in the linking information and balise groups marked as unlinked shall be taken into account.
\\
&
\begin{itemize}
\item A message is still complete and correct, if a telegram is missing (or not decoded or incompletely decoded), and this telegram is duplicated within the balise group and the duplicating one is correctly read.
\item In case of multiple balises, the order of the balises must be either ascending (nominal) or descending (reverse).
\item A message is not correct, if a message counters (M\_MCOUNT) equals 254 (that means: The telegram never fits any message of the group). A message counter can  equal 255 (that means: The telegram fits with all telegrams of the same balise group) and all other values must be the same.
\end{itemize}

The orientation of the BG and the running direction of the train are calculated in this block.When linking information is used on-board, the check, if the message of linked balise group has been received in due time and at the expected location, will be performed in "Calculate Train Position". The checks on the validity of the data in the packets and the validity with respect to the direction of motion
will be performed in other modules, e.g. "ValidateDataDirection".\\
\midrule
Input documents	& 
Subset-026, Chapter 7 and 8: Definition of the Balise Telegram\newline
Subset-026, Chapter 3.4.1-3, 3.16.2: Handling of Balise Telegrams\newline
Subset-026, Chapter 3.16.2: Check of the balise group\newline
Subset-026, Chapter 4.5.2: Active Functions Table\\
\midrule
Safety integrity level	& 4 \\
\midrule
Time constraints		& n/a \\
\midrule
API requirements 		& n/a \\
\bottomrule
\end{longtable}


\paragraph{Interface}

For an overview of the interface of this internal component we refer to the SCADE model (cf.~link above) respectively the SCADE generated documentation.
