%set the master document for easy compilation
%!TEX root = ../D3_5_3.tex

\paragraph{Component Requirements}

\begin{longtable}{p{.25\textwidth}p{.7\textwidth}}
\toprule
Component name			& TargetManagement \\
\midrule
Link to SCADE model		& {\footnotesize \url{https://github.com/openETCS/modeling/tree/master/model/Scade/System/ObuFunctions/SpeedSupervison/TargetManagement}} \\
\midrule
SCADE designer			&  Benjamin Beichler, University of Rostock\newline
Thorsten Schulz, University of Rostock \\
\midrule
Description				& This operator calculates/updates the list of targets to be supervised by SDM. Taking the current movement authority, the most restrictive speed profile and the current maximum safe front end position as an input, the operator outputs a list of MRSP-Targets and a Limit-of-Authority-Target (LoA) or, if an End of Authority is known, the End-of-Authority-Target (EoA) and the Supervised Location (SvL). Since LoA and SvL are mutually exclusive but both result in a trip-target, they use the same flow.

\subparagraph*{Derivation of Targets from Movement Authority}
The \emph{Movement Authority} creates three types of targets:
\begin{description}
\item[Limit of Authority (LoA)] if the End of Authority is not yet known to the RBC and is accompanied by a speed limit for the given location.
\item[End Of Authority (EoA)] requires the train to stop and creates a Service Brake Target
\item[Supervised Location (SvL)] is derived from the EoA but results in an emergency brake target and on passing in a trip. The SvL may be offset from the EoA to the Overlap (OL) or the Dangerpoint (DP).
\end{description}

\subparagraph*{Derivation of Targets from MRSP}
According to \cite[Chapt.~3.13.8.2]{subset-026}, every speed decrease of the MRSP is used to derive a target. Therefore in every cycle in which the MRSP is updated, the operator iterates through the entire MRSP searching for all MRSP targets. For this purpose, every element of the MRSP is compared with its successor.

\subparagraph*{Update of Targets}
In every cycle the operator monitors whether all targets are already passed. To this end, it iterates over the list of targets comparing the current front end position with the target's location. \\
\midrule
Input documents	& 
Subset-026, Chapter 3.13.8.2: Determination of the supervised targets \\
\midrule
Safety integrity level		& 4 \\
\midrule
Time constraints		& n/a \\
\midrule
API requirements 		& n/a \\
\bottomrule
\end{longtable}


\paragraph{Interface}

For an overview of the interface of this internal component we refer to the SCADE model (c.f.~link above) respectively the SCADE generated documentation.