\documentclass{template/openetcs_article}
% Use the option "nocc" if the document is not licensed under Creative Commons
%\documentclass[nocc]{template/openetcs_article} 
\usepackage{lipsum,url}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{fixme}
\usepackage{lscape} 
\usepackage{pgfgantt}
\usepackage{adjustbox}
\usepackage{datetime}



%user specified macros
%\input{macros.tex}


\graphicspath{{./template/}{.}{./images/}}
\begin{document}
\frontmatter
\project{openETCS}

%Please do not change anything above this line
%============================
% The document metadata is defined below

%assign a report number here
\reportnum{OETCS/WP3/DescriptionOfWork}

%define your workpackage here
\wp{Work Package 3: ``Modelling''}

%set a title here
\title{openETCS Modelling Work Package}

%set a subtitle here
\subtitle{Description of Work}

%set the date of the report here
\date{January 2014}

%define a list of authors and their affiliation here

\author{openETCS WP3 SRS task force}

\affiliation{The Team}
 
%\author{Jan Welte}

%\affiliation{WP3 Safety and Requirements Traceability}

\author{Marielle Petit-Doche}

\affiliation{Methodology}

\author{Uwe Steinke}

\affiliation{Objects)}

\author{Bernd Hekele}

\affiliation{SRS Findings)}

% define the coverart
\coverart[width=350pt]{openETCS_EUPL}

%define the type of report
\reporttype{Description of work}



\begin{abstract}
%define an abstract here

  This work package...



\end{abstract}

%=============================
%Do not change the next three lines
\maketitle
\tableofcontents
\listoffiguresandtables
\newpage
%=============================

% The actual document starts below this line
%=============================


%Start here



%-----------------------------------------------------------------------
\section{Introduction}
%-----------------------------------------------------------------------

\input{sections/introduction.tex}

\input{sections/objectives.tex}

\subsection{Organisation of the Work package}

Due to historical reasons we have some projects linked to the openETCS modeling activities.
In the progress of our task we will make a clean-up on the history. Here is an overview on the different repositories with reasonable content.

\begin{itemize}
\item \url{https://github.com/openETCS/modeling}\\
The modeling repository is the place where modeling takes place. openETCS ToolChain is linked to this repository (folder "model". All code artefacts have to reside in this location. 


\item \url{https://github.com/openETCS/SRS-Analysis}\\
The SRS-Analysis Repository was originally introduced to support the task force led by Alstom and intended to start with the analysis work.
In this location you can find traces of the analysis work. The repository is still in use.

\item \url{https://github.com/openETCS/dataDictionary}\\
The data-Dictionary repository is related to the definition of common data and functions. The dataDictionry implementation is based on SysML/Papyrus. Therefore, not tools nor tool artefacts are stored here. Only documentation is needed. The repository is still in use.

\item \url{https://github.com/openETCS/SSRS}\\
The SSRS activities had been used before the modelling kick-off to prepare for the analysis work. There are stil some useful documents included. Especially the wiki is usefull.
However, the place is no longer used for active work and the repository can - after having moved valid information to other locations - be considered to be recycled.

\item Requirements on Process and Methods, Guidelines\\
The following guidelines are the basis for modeling work:
The openETCS development process: \url{https://github.com/openETCS/requirements/blob/master/D2.3/D2_3.pdf}\\
The openETCS requirements on methods: \url{https://github.com/openETCS/requirements/blob/master/D2.4/D2_4.pdf} 
This document also describes naming conventions which you need to respect for working in this task.

\end{itemize}


\input{sections/methodology.tex}

\section{Verification and Validation of Modeling artefacts}
The handling is based on the openETCS review process which is documented as an extension of the quality insurance plan. \url{https://github.com/openETCS/governance/tree/master/Review%20Process}.
In short, this is done in posting an issue with the issue tracker of the modeling repository. 
Before passing the artefact to WP4, the WP3 product owner has to agree to the triggering of verification and validation.

\input{sections/Findings.tex}

\nocite{*}
%===================================================
%Do NOT change anything below this line

\end{document}
